\documentclass[14pt]{exam}
\usepackage[utf8]{inputenc}

\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{siunitx}
\usepackage{multicol}

\newcommand{\class}{Physics 9}
\newcommand{\term}{Numericals Test}
\newcommand{\examnum}{Test No. 2}
\newcommand{\examdate}{17/04/2021}
\newcommand{\timelimit}{45 Minutes}

\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule


\begin{document}

\noindent
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r @{\extracolsep{6pt}} l}
\textbf{\class} & \textbf{Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} & Teacher & \makebox[2in]{\hrulefill}
\end{tabular*}\\
\rule[2ex]{\textwidth}{2pt}

This exam contains \numpages\ pages (including this cover page) and \numquestions\ questions.\\
Total of points is \numpoints.


\begin{center}
Grade Table (for teacher use only)\\
\addpoints
\gradetable[v][questions]
\end{center}

\noindent
\rule[2ex]{\textwidth}{2pt}

\begin{questions}

\question[10] At what altitude the value of $g$ would become one fourth than on the surface of the Earth?

\question[10] Two lead spheres each of mass $1000 \ kg$ are kept with their centres $1 \ m$ apart. Find the gravitational force with which they attract each other.

\addpoints
\question[2] \textbf{Encircle the correct answer from the given choices:} \\
The value of g at a height one Earth's radius above the surface of the Earth is:
\addpoints
\begin{checkboxes}
\choice $2g$
\choice $\frac{1}{2} \ g$
\choice $\frac{1}{3} \ g$
\choice $\frac{1}{4} \ g$
\end{checkboxes}

\question[10] A stone of mass $500 \ g$ strikes the ground with a velocity of $20 \ ms^{-1}$. How much is the kinetic energy of the stone at the time it strikes the ground?
\addpoints

\question[5] A body of mass $50 \ kg$ is raised to a height of $3 \ m$. What is its potential energy?
\addpoints

\question[2] \textbf{Encircle the correct answer from the given choices:} \\
The work done will be zero when the angle between the force and the distance is
\addpoints
\begin{checkboxes}
\choice $45^{\circ}$
\choice $60^{\circ}$
\choice $90^{\circ}$
\choice $180^{\circ}$
\end{checkboxes}

\question[10] A $500 \ g$ stone is thrown up with a velocity of $15 \ ms^{-1}$. Find its (i) P.E. at its maximum height (ii) K.E. when it hits the ground
\addpoints

\question[5] The head of a pin is a square of side $10 \ mm$. Find the pressure on it due to a force of $20 \ N$.
\addpoints

\question[20] A force of $200 \ N$ acts on a body of mass $20 \ kg$. The force accelerates the body from rest until it attains a velocity of $50 \ ms^{-1}$. Through what distance the force acts?
\addpoints

\question[1] \textbf{Encircle the correct answer from the given choices:} \\
What will be the value of $\beta$ for a solid for which $\alpha$ has a value of $\num{2e-5} \ K^{-1}$?
\addpoints
\begin{checkboxes}
\choice $\num{2e-5} \ K^{-1}$
\choice $\num{6e-5} \ K^{-1}$
\choice $\num{8e-15} \ K^{-1}$
\choice $\num{8e-5} \ K^{-1}$
\end{checkboxes}

\question[5] Temperature of water in a beaker is $50^{\circ}$. What is its value in Fahrenheit scale?
\addpoints

\question[10] Normal human body temperature is $98.6^{\circ}$. Convert it into Celsius scale and Kelvin scale.
\addpoints

\question[10] The diameter of the piston of a hydraulic press is $30 \ cm$ How much force is required to lift a car weighing $20,000 \ N$ on its piston if the diameter of the piston of the pump is $3 \ cm$?
\addpoints

%\fillwithdottedlines{8em}

\end{questions}

\end{document}
